---
output: github_document
always_allow_html: true
editor_options: 
  markdown: 
    wrap: 72
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(tidyverse)
```

# grdwtrsmpkwale

<!-- badges: start -->

[![License: CC BY
4.0](https://img.shields.io/badge/License-CC_BY_4.0-lightgrey.svg)](https://creativecommons.org/licenses/by/4.0/)
[![R-CMD-check](https://github.com/openwashdata/grdwtrsmpkwale/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/openwashdata/grdwtrsmpkwale/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of `grdwtrsmpkwale` is to provide datasets for research and
planning of water and solid waste management in Kwale, Kenya. This
package includes water anlaysis data collected in 2016 combined with the
geospatial data from the collection points.

## Installation

You can install the development version of 'grdwtrsmpkwale' from
[GitHub](https://github.com/openwashdata/grdwtrsmpkwale) with:

``` r
# install.packages("devtools")
devtools::install_github("openwashdata/grdwtrsmpkwale")
```

Alternatively, you can download the individual datasets as CSV or XLSX
file from the table below.

```{r echo=FALSE, message=FALSE, warning=FALSE}

extdata_path <- "https://github.com/openwashdata/grdwtrsmpkwale/raw/main/inst/extdata/"

read_csv("data-raw/dictionary.csv") |> 
  distinct(file_name) |> 
  mutate(file_name = str_remove(file_name, ".rda")) |> 
  rename(dataset = file_name) |> 
  mutate(
    CSV = paste0("[Download CSV](", extdata_path, dataset, ".csv)"),
    XLSX = paste0("[Download XLSX](", extdata_path, dataset, ".xlsx)")
  ) |> 
  knitr::kable()

```

# Data

This data package has two datasets: `water_samples` and
`selected_samples`.

```{r}
library(grdwtrsmpkwale)
```

## water_samples

DATA DESCRIPTION

The `water_samples` data set has `r ncol(water_samples)` variables and
`r nrow(water_samples)` observations. For an overview of the variable
names, see the following table.

```{r, eval=FALSE}
water_samples
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
readr::read_csv("data-raw/dictionary.csv") |>
  dplyr::filter(file_name == "water_samples.rda") |>
  dplyr::select(variable_name:error) |> 
  knitr::kable() |> 
  kableExtra::kable_styling() |> 
  kableExtra::scroll_box()
```

##  selected_samples

DATA DESCRIPTION

The `selected_samples` data set has `r ncol(selected_samples)` variables
and `r nrow(selected_samples)` observations. For an overview of the
variable names, see the following table.

```{r, eval=FALSE}
selected_samples
```

```{r echo=FALSE, message=TRUE, warning=FALSE}
readr::read_csv("data-raw/dictionary.csv") |> 
  dplyr::filter(file_name == "selected_samples.rda") |> 
  dplyr::select(variable_name:error) |>  
  knitr::kable() |> 
  kableExtra::kable_styling() |> 
  kableExtra::scroll_box()
```

## Example (TBD)

Write a demo snippet here.

```{r}
```

# License

Data are available as
[CC-BY](https://github.com/openwashdata/grdwtrsmpkwale/blob/main/LICENSE.md).

# Citation

```{r echo=FALSE}
citation("grdwtrsmpkwale")
```

## Related References (TBD)
